---
title: "SS2864GroupProj"
author: "Rui Zhu"
date: "11/23/2020"
output: html_document
---

\newpage
# Andern's work 11/24/20
```{r}
library(magrittr) 
library(ggplot2)
library(mapcan)
library(dplyr)
#data from 1/22/20 till 11/22/20
df <- read.csv(file = 'time_series_covid19_confirmed_global.csv')
head(df)

#And then we trim the dataframe a little bit before we utilize it for the first task 

df = df[-(42:43),]
df =df[40:52,]
print(df)


df = df[c("Province.State","X11.23.20")]
#use mapcan
pr_map <- mapcan(boundaries = province,
       type = standard) %>%
  ggplot(aes(x = long, y = lat, group = group))
pr_map <- pr_map +
  geom_polygon() +
  coord_fixed()
pr_geographic <- mapcan(boundaries = province,
       type = standard)


pr_geographic <- inner_join(pr_geographic, 
           df, 
           by = c("pr_english" = "Province.State"))
pr_geographic %>%
  ggplot(aes(x = long, y = lat, group = group, fill = X11.23.20)) +
  geom_polygon() +
  coord_fixed() +
  theme_mapcan() +
  scale_fill_viridis_c(name = "X11.23.20") +
  ggtitle("Canadian Confirmed Cases by Province")

#global histogram 
df <- read.csv(file = 'time_series_covid19_confirmed_global.csv')
df=df[0:310]
df
df= colSums(df[,-(1:4)])
plot(df)
#canada histogram
df2 <- read.csv(file = 'time_series_covid19_confirmed_global.csv')
df2 =df2[40:54,]
df2= colSums(df2[,-(1:4)])
plot(df2)
```
  * The ggplot indicates that the number of confirmed cases decreases from two sided of the border honrizontally.  
  * The ggplot indicates that Ontario and Quebec are two provinces with most cumulative confirmed cases.
  

\newpage
# Second Part
  * Therefore, we make the hypothesis that keeping all other factors unchanged, the norther wherever is, it has less confirmed cases(Simple hypothesis, should not be hard to test)
```{r}
library(tidyverse)
library(caret)
df <- read.csv(file = 'time_series_covid19_confirmed_US.csv')
df = df[c(9,10,317)]
df
train.control <- trainControl(method = "LOOCV")
model <- train(X11.22.20 ~., data = df, method = "lm",
               trControl = train.control)

print(model)


#lat only
df <- read.csv(file = 'time_series_covid19_confirmed_US.csv')
df = df[c(9,317)]
df
train.control <- trainControl(method = "LOOCV")
model <- train(X11.22.20 ~., data = df, method = "lm",
               trControl = train.control)
print(model)

#Or maybe I should just fit into a simple linear regression model, LOOCV might be way too strict
df2 <- read.csv(file = 'time_series_covid19_confirmed_US.csv')
df2 = df2[c(9,10,317)]
reg = lm(X11.22.20 ~Lat+Long_, data = df2)
summary(reg)
```
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  